Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-09-04 manu-draft.qmd
add total fo to fig 1
added spei/spi data and fig for meteo and wq trends

Observed trends aggregated by year and bay segment across stations and months in @fig-saltempraw.

@@

![Seagrass changes over time in Tampa Bay for (a) areal coverage and (b) frequency occurrence of major species. Changes are shown for major bay segments. Note the different time scale between (a) and (b). Coverage maps in (a) began in 1988 and seagrass transect monitoring in (b) began in 1998. Red lines in (a) show approximate capacity of seagrass coverage based on the baywide target of 40,000 acres. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/seagrasschg.png){#fig-seagrasschg}

@@

![Long-term salinity and temperature trends for major bay segments from 1975 to 2022. Points are colored by sampling location in the water column. Points show the average and 95% confidence interval across all stations and sampling months for each year in each bay segment. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/saltempraw.png){#fig-saltempraw}

>>>>

Observed trends aggregated by year and bay segment across stations and months in @fig-meteowqraw.

@@

![Seagrass changes over time in Tampa Bay for (a) areal coverage and (b) frequency occurrence of major species. Changes are shown for major bay segments. Note the different time scale between (a) and (b); coverage maps in (a) began in 1988 and seagrass transect monitoring in (b) began in 1998. Red lines in (a) show approximate capacity of seagrass coverage based on the baywide target of 40,000 acres. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/seagrasschg.png){#fig-seagrasschg}

@@

![Long-term precipitation, hydrologic load, Standard Precipitation Index (SPI), air temperature, salinity, and water temperature trends from 1975 to 2022. Points for salinity and water temperature are colored by sampling location in the water column and show the average (95% confidence interval) across all stations and sampling months for each year in each bay segment. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/meteowqraw.png){#fig-meteowqraw}
